Explore tumor cell classification with CellAssign

### 2024-05-02 analyses/ewings-cell-type/02-cellassign-tumor-cell-classification.Rmd
formatting fixes

We use `CellAssign` with a variety of references: 
- A full list of tumor marker genes only. 
- A filtered list of tumor marker genes only. 
- Tumor marker genes and non-tumor marker genes from [Visser et al.](https://doi.org/10.1158/2767-9764.CRC-23-0027) specified in the supplemental methods. 
- Tumor marker genes and marker genes from endothelial cells and fibroblast marker genes in PanglaoDB.

@@

```{r packages}
suppressMessages(
  # load required packages
  library(SingleCellExperiment),
  library(ggplot2)
)
```

@@

ComplexHeatmap::Heatmap(
  t(jaccard_mtx), # transpose because matrix rows are in common & we want a vertical arrangement
  col = circlize::colorRamp2(c(0, 1), colors = c("white", "darkslateblue")),
  border = TRUE,
  ## Row parameters
  cluster_rows = FALSE,
  row_title = "Marker gene",
  row_title_gp = grid::gpar(fontsize = 12),
  row_title_side = "left",
  row_names_side = "left",
  row_dend_side = "right",
  row_names_gp = grid::gpar(fontsize = 10),
  ## Column parameters
  cluster_columns = FALSE,
  column_title = "CellAssign",
  column_title_gp = grid::gpar(fontsize = 12),
  column_names_side = "bottom",
  column_names_gp = grid::gpar(fontsize = 10),
  column_names_rot = 90,
  ## Legend parameters
  heatmap_legend_param = list(
    title = "Jaccard index",
    direction = "vertical",
    legend_width = unit(1.5, "in")
  ),
  show_heatmap_legend = TRUE,
)
```
As expected, it looks like CellAssign is assigning very few cells to tumor that overlap with the tumor cells annotated with marker gene analysis. 
It looks like most tumor cells are being classified as normal with the marker gene analysis.

@@

# for each cell type, plot each individual marker as a UMAP 
celltypes |> 
  purrr::walk(\(celltype){
    plot_df <- marker_gene_exp_df |> 
      dplyr::filter(cell_type == celltype)

>>>>

We use `CellAssign` with a variety of references:

- A full list of tumor marker genes only. 
- A filtered list of tumor marker genes only. 
- Tumor marker genes and non-tumor marker genes from [Visser et al.](https://doi.org/10.1158/2767-9764.CRC-23-0027) specified in the supplemental methods. 
- Tumor marker genes and marker genes from endothelial cells and fibroblast marker genes in PanglaoDB.

@@

```{r packages}
suppressPackageStartupMessages({
  # load required packages
  library(SingleCellExperiment)
  library(ggplot2)
})
```

@@

ComplexHeatmap::Heatmap(
  t(jaccard_mtx), # transpose because matrix rows are in common & we want a vertical arrangement
  col = circlize::colorRamp2(c(0, 1), colors = c("white", "darkslateblue")),
  border = TRUE,
  ## Row parameters
  cluster_rows = FALSE,
  row_title = "Marker gene",
  row_title_gp = grid::gpar(fontsize = 12),
  row_title_side = "left",
  row_names_side = "left",
  row_dend_side = "right",
  row_names_gp = grid::gpar(fontsize = 10),
  ## Column parameters
  cluster_columns = FALSE,
  column_title = "CellAssign",
  column_title_gp = grid::gpar(fontsize = 12),
  column_names_side = "bottom",
  column_names_gp = grid::gpar(fontsize = 10),
  column_names_rot = 90,
  ## Legend parameters
  heatmap_legend_param = list(
    title = "Jaccard index",
    direction = "vertical",
    legend_width = unit(1.5, "in")
  ),
  show_heatmap_legend = TRUE,
)
```

As expected, it looks like CellAssign is assigning very few cells to tumor that overlap with the tumor cells annotated with marker gene analysis. 
It looks like most tumor cells are being classified as normal with the marker gene analysis.

@@

# for each cell type, plot each individual marker as a UMAP 
celltypes |> 
  purrr::map(\(celltype){
    plot_df <- marker_gene_exp_df |> 
      dplyr::filter(cell_type == celltype)
